#MSDS Spring 2018 
##DATA 607 Data Aquisition and Management
####Jiadi Li
####Week 1 Assignment: Basic Loading and Transformation

###Task: Create a data frame with a subset of the columns in the dataset. Add meaningful column names and replace the abbreviations.

1. Place the file in Github and load the data.
```{r}
Mushroom <- read.csv("https://raw.githubusercontent.com/xiaoxiaogao-DD/Spring2018_DATA607_Assignment1/master/mushroom.csv",header = FALSE)
summary(Mushroom)
```

2. Subset and rename column
```{r}
Mushroom_cap <- subset(Mushroom,select = c(V2,V3,V4,V1))
colnames(Mushroom_cap)[1] <- "shape"
colnames(Mushroom_cap)[2] <- "surface"
colnames(Mushroom_cap)[3] <- "color"
colnames(Mushroom_cap)[4] <- "classes"
summary(Mushroom_cap)
```
3. Rename attributes for classes
```{r}
Mushroom_cap$classes <- as.character(Mushroom_cap$classes)
Mushroom_cap$classes[Mushroom_cap$classes=="e"]<- "edible"
Mushroom_cap$classes[Mushroom_cap$classes=="p"]<- "poisoneous"
Mushroom_cap$classes <- as.factor(Mushroom_cap$classes)
```

4. Rename attributes for shape
```{r}
Mushroom_cap$shape <- as.character(Mushroom_cap$shape)
Mushroom_cap$shape[Mushroom_cap$shape=="b"]<- "bell"
Mushroom_cap$shape[Mushroom_cap$shape=="c"]<- "conical"
Mushroom_cap$shape[Mushroom_cap$shape=="f"]<- "flat"
Mushroom_cap$shape[Mushroom_cap$shape=="k"]<- "knobbed"
Mushroom_cap$shape[Mushroom_cap$shape=="s"]<- "sunken"
Mushroom_cap$shape[Mushroom_cap$shape=="x"]<- "convex"
Mushroom_cap$shape <- as.factor(Mushroom_cap$shape)
```

5. Rename surface
```{r}
Mushroom_cap$surface <- as.character(Mushroom_cap$surface)
Mushroom_cap$surface[Mushroom_cap$surface=="f"]<- "fibrous"
Mushroom_cap$surface[Mushroom_cap$surface=="g"]<- "grooves"
Mushroom_cap$surface[Mushroom_cap$surface=="s"]<- "smooth"
Mushroom_cap$surface[Mushroom_cap$surface=="y"]<- "scaly"
Mushroom_cap$surface <- as.factor(Mushroom_cap$surface)
```

6. Rename color
```{r}
Mushroom_cap$color <- as.character(Mushroom_cap$color)
Mushroom_cap$color[Mushroom_cap$color=="n"]<- "brown"
Mushroom_cap$color[Mushroom_cap$color=="g"]<- "gray"
Mushroom_cap$color[Mushroom_cap$color=="e"]<- "red"
Mushroom_cap$color[Mushroom_cap$color=="y"]<- "yellow"
Mushroom_cap$color[Mushroom_cap$color=="w"]<- "white"
Mushroom_cap$color[Mushroom_cap$color=="b"]<- "buff"
Mushroom_cap$color <- as.factor(Mushroom_cap$color)
summary(Mushroom_cap)
```







































